InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex

>>>>

As a second image generative model we use Dall-E from OpenaAI (\url{https://openai.com/dall-e-3}). Dall-E works by modelling text and image tokens as a single data stream. This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.

This is done in two steps: 
\begin{enumerate}
	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
\end{enumerate}

The exact procedure proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
